---
title: "Tanner Crab Simulation - work in progress- DRAFT"
author: "Katie Palof"
date: "May 19th, 2016"
output: html_document
---

In a response to budget constraints, that may yield a decrease in survey areas being evaluated annually, simulations were performed to determine the influence of various survey adjustments on the regional biomass estimate.  These were evaluated for both legal and mature biomass.  The results reported here are for the estimates of total legal and mature biomass for the SE Region - they include both survey and non-survey biomass. Biomass from surveyed areas is calculated using survey CPUE and a catch-survey-analysis (CSA) model, whereas non-surveyed area biomass is expanded from the estimate of surveyed areas. 
The goal of these simulations was to determine the probably effect of removing survey areas on the estiamte of total biomass.  



### Data Used
The biomass data used in these simulations is taken from the sigma plot 'bay by bay' documents for legal biomass from each area and from the individual CSA models (historic excel files) for mature biomass from each area.  They are slightly different from those biomasses reported in annual stock health documents but are the most accurate and complete.  To better match historically reported biomasses, estimates for Glacier Bay, Thomas Bay, Port Camden, and Holkham Bay for early years without a survey were estimated to be the minimium from the survey start until 2012. These are referred to in this document as adjusted biomass estimates of legal and mature crab. 

The expansion percentage used from 2001 until 2014 designated 71% of the tanner biomass to be from the survey areas while 29% was from non-surveyed areas.  This percentage was calculated form historic (1980-2000) harvest records. 
It was thought that when removing survey areas that this expansion would be adjusted by the percent contribution of that survey area to historic harvest.  However, this drastically changed the biomass estimates due to the historic harvest percentages being different from each survey area's actual contribution to the biomass in most years.  Therefore, the contribution of each survey areas to the estimate of biomass was calculated for the last 10 years of the survey (2005-2015).  This percent contribution, scaled to a total of 71%, was used to in these simulations to determine the expansion factor for each area if it was removed from the survey.  

In each simulation the areas surveyed were set for all years.  Historic survey biomass was used for these areas and the overall percent contribution was determined by summing the percent contribution for each area.  Each simulation therefore, results in a time series of total biomass estimates where the survey biomass component only uses areas designated in the simulation and the non-survery biomass is expanded from the calculated survey biomass.  The simulation does NOT currently allow for variation between years of the survey areas sampled, this would be the next step.  The total biomass time series was then compared to the "known" time series (K) of total biomass.  This comparison is represented visually in a figure for each simulation (S) and as an average percent difference from the known biomass (Table 3). 



```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE, warning = FALSE}
library(plyr)
library(dplyr)
library(stringr)
library(ggplot2)
library(tidyr)
library(reshape2)
library(extrafont)
library(ggthemes)
library(knitr)
library(pander)
#set graphing theme
loadfonts(device="win")
windowsFonts(Times=windowsFont("TT Times New Roman"))
theme_set(theme_bw(base_size = 12, base_family = 'Times New Roman')+ 
            theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank()))

#setwd("C:/Users/kjpalof/Documents/R projects/survey-cut-sim_kp")
dat_adj <- read.csv("C:/Users/kjpalof/Documents/R projects/survey-cut-sim_kp/data/tanner crab data_legal_adj.csv") # biomass by year and survey area
percent <- read.csv("C:/Users/kjpalof/Documents/R projects/survey-cut-sim_kp/data/tanner crab percent.csv") # file with the percent contribution for each area
dat_mature_adj <-read.csv("C:/Users/kjpalof/Documents/R projects/survey-cut-sim_kp/data/tanner crab data_mature_adj.csv") 
# adjusted to accomidate how early biomasses were calculated in areas not surveyed.

#### Legal- combine two data sets
dat_adj %>%
  right_join(percent, by="SurveyArea") -> dat4

dat4 %>%
  mutate(percent_real = ifelse (Biomass_lb > 0, percent_survey_area, 0)) %>%
  group_by(Year_Survey) %>%
  # want to exclude areas that do not have biomass estimates
  summarize(expansion = sum (percent_real, na.rm=T), survey_biomass = sum (Biomass_lb, na.rm =T)) %>%
  # summarizes the expansion for each year based on the areas with  biomass estimates
  mutate(non_biomass = (survey_biomass / expansion) - survey_biomass, total_lb = survey_biomass + non_biomass) -> known_dat_survey_adj

### Mature - combine two data sets
#####
dat_mature_adj %>%
  right_join(percent, by="SurveyArea") -> dat5
#head(dat5)
# using percent for each area from the last 10 years of the survey - percent_survey_area
dat5 %>%
  mutate(percent_real = ifelse (Biomass_lb > 0, mature_survey_percent, 0)) %>%
  group_by(Year_Survey) %>%
  # want to exclude areas that do not have biomass estimates
  summarize(expansion = sum (percent_real, na.rm=T), survey_biomass = sum (Biomass_lb, na.rm =T)) %>%
  # summarizes the expansion for each year based on the areas with  biomass estimates
  mutate(non_biomass = (survey_biomass / expansion) - survey_biomass, total_lb = survey_biomass + non_biomass) -> known_mature_survey_adj

```

### Known biomass from CSA models (using survey CPUEs)

#### Table 1: Legal Biomass and expansion factors 
```{r pander, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, comment=""}
#head(dat2)
# using percent for each area from the last 10 years of the survey - percent_survey_area
panderOptions("digits", 2)
pander(known_dat_survey_adj)
#ls()
```


#### Figure 1: 
```{r figure, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, comment=""}
ggplot(known_dat_survey_adj, aes(Year_Survey, total_lb)) + geom_point(size=2) +geom_smooth() +
  scale_color_tableau() +
  scale_x_continuous(breaks = seq(1996, 2016, 2))+ scale_y_continuous(breaks = seq(0, 60000000, 1000000))+
  coord_cartesian(ylim=c(0,6000000)) +
  xlab('Survey Year') + ylab('Total LEGAL biomass adj')+
  ggtitle('Tanner crab total LEGAL biomass (survey and non)')
```


#### Table 2: Mature Biomass and expansion factors 
```{r pander2, echo = FALSE, comment=""}
#head(dat2)
# using percent for each area from the last 10 years of the survey - percent_survey_area
panderOptions("digits", 2)
pander(known_mature_survey_adj)
#ls()
```

#### Figure 2: 
```{r figure2, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, comment=""}
ggplot(known_mature_survey_adj, aes(Year_Survey, total_lb)) + geom_point(size=2) +geom_smooth() +
  scale_color_tableau() +
  scale_x_continuous(breaks = seq(1996, 2016, 2))+ scale_y_continuous(breaks = seq(0, 80000000, 1000000))+
  coord_cartesian(ylim=c(0,8000000)) +
  xlab('Survey Year') + ylab('Total MATURE biomass adj')+
  ggtitle('Tanner crab total MATURE biomass (survey and non)')

```

```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE}
# set up for survey simulations
areas_all <- c("EI" , "GB" , "GLB" ,"HB"  ,"ICY" ,"LS",  "NJ" , "PB" , "PC" , "PF" , "PS",  "SC" , "SP" , "TB")
areas_2015 <- c("EI" , "GB" , "GLB" ,"HB"  ,"ICY" ,"LS",  "NJ" , "PB" , "PS",  "SC" , "SP" , "TB")
  ### those used in 2015 
areas_RKC_only <-c("EI", "GB", "LS", "NJ", "PB", "PS", "SC", "SP")
  ### only the RKC survey areas.
areas_1 <- c("EI" , "GB" , "GLB" ,"ICY" ,"LS",  "NJ" , "PB" , "PS",  "SC" , "SP" )
  #2015 areas minus "TB", "HB" or leg 2

#using the last 10 years of survey biomass for each area to calculate percent contribution
# currently uses legal % expansion from survey see next function for mature
survey_sim <- function(df, areas_used) {
  df %>%
    mutate(percent_usedA = ifelse(SurveyArea %in% areas_used, percent_survey_area, 0)) %>%
    mutate(percent_used = ifelse(Biomass_lb >0, percent_usedA, 0)) %>%
    #only want to use biomass from areas that are included in the sim
    mutate(biomass_used = ifelse(SurveyArea %in% areas_used, Biomass_lb, 0)) %>%
    group_by(Year_Survey) %>%
    # want to exclude areas that do not have biomass estimates
    summarize(expansion = sum (percent_used, na.rm=T), survey_biomass = sum (biomass_used, na.rm =T)) %>%
    # summarizes the expansion for each year based on the areas with  biomass estimates
    # need to add type for graphing K = known data
    mutate(non_biomass = (survey_biomass / expansion) - survey_biomass, total_lb = survey_biomass + non_biomass, type = "S") -> sim2
  df %>%
    mutate(percent_real = ifelse (Biomass_lb > 0, percent_survey_area, 0)) %>%
    group_by(Year_Survey) %>%
    # want to exclude areas that do not have biomass estimates
    summarize(expansion = sum (percent_real, na.rm=T), survey_biomass = sum (Biomass_lb, na.rm =T)) %>%
    # summarizes the expansion for each year based on the areas with  biomass estimates
    # need to add type for graphing 
    mutate(non_biomass = (survey_biomass / expansion) - survey_biomass, total_lb = survey_biomass + non_biomass, type = "K") -> known_dat_survey
  out <- rbind(known_dat_survey, sim2)
  out %>%
    # want to add a percent difference column 
    mutate (diff = ifelse( type == "K", 0, (sim2$total_lb  - known_dat_survey$total_lb)), per_diff = 
              ifelse( type == "K", 0, ((sim2$total_lb  - known_dat_survey$total_lb)/ known_dat_survey$total_lb))) 

}

# mature percent for expansion used here
survey_sim_mature <- function(df, areas_used) {
  df %>%
    mutate(percent_usedA = ifelse(SurveyArea %in% areas_used, mature_survey_percent, 0)) %>%
    mutate(percent_used = ifelse(Biomass_lb >0, percent_usedA, 0)) %>%
    #only want to use biomass from areas that are included in the sim
    mutate(biomass_used = ifelse(SurveyArea %in% areas_used, Biomass_lb, 0)) %>%
    group_by(Year_Survey) %>%
    # want to exclude areas that do not have biomass estimates
    summarize(expansion = sum (percent_used, na.rm=T), survey_biomass = sum (biomass_used, na.rm =T)) %>%
    # summarizes the expansion for each year based on the areas with  biomass estimates
    # need to add type for graphing K = known data
    mutate(non_biomass = (survey_biomass / expansion) - survey_biomass, total_lb = survey_biomass + non_biomass, type = "S") -> sim2
  df %>%
    mutate(percent_real = ifelse (Biomass_lb > 0, mature_survey_percent, 0)) %>%
    group_by(Year_Survey) %>%
    # want to exclude areas that do not have biomass estimates
    summarize(expansion = sum (percent_real, na.rm=T), survey_biomass = sum (Biomass_lb, na.rm =T)) %>%
    # summarizes the expansion for each year based on the areas with  biomass estimates
    # need to add type for graphing 
    mutate(non_biomass = (survey_biomass / expansion) - survey_biomass, total_lb = survey_biomass + non_biomass, type = "K") -> known_dat_survey
  out <- rbind(known_dat_survey, sim2)
  out %>%
    # want to add a percent difference column 
    mutate (diff = ifelse( type == "K", 0, (sim2$total_lb  - known_dat_survey$total_lb)), per_diff = 
              ifelse( type == "K", 0, ((sim2$total_lb  - known_dat_survey$total_lb)/ known_dat_survey$total_lb))) 
  
}
```

### Simulation 1: 2015 survey areas, removed Port Camden and Port Frederick 
For the 2015 survey season the areas of Port Camden and Port Frederick were removed from the surveyed areas.  In the 2015 assessment these areas were considered part of the non-surveyed biomass.  This simulation was done to determine the overall influence of these areas on total biomass for the entire time series.  Prior to performing these simulations it was determined that these areas were very small contributors to the survey and most likely did not play a large role in determining total biomass. 

These results were validated in the simulation.  The total biomass time series was nearly identical to that using all of the survey areas.  

Average percent difference for legal biomass in Sim 1 (this should be read as 0.38%)
```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE,  comment =""}
sim2015_adj <- survey_sim (dat4, areas_2015)
#paste("Average", "percent", "difference", "for", "legal", "biomass")
round(mean (sim2015_adj$per_diff[20:38])*100, 4)
```
Average percent difference for mature biomass in Sim 1
```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE,  comment =""}
#ls()
sim2015mature_adj <- survey_sim_mature (dat5, areas_2015)
round(mean (sim2015mature_adj$per_diff[20:38])*100,4)

```

The total biomass for both legal and mature crab from Simulation 1 (S) is visually represented in the figures below (Figure 3 & 4), along with the total biomass from the "known (K)" survey data. Simulation 1 mirrors those survey areas used in the 2015 survey by excluding both Port Camden and Port Frederick.

#### Figure 3:
```{r figure3, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, comment=""}
ggplot(sim2015_adj, aes(Year_Survey, total_lb, color = type)) + geom_point(size=2) +geom_smooth() +
  scale_color_tableau() +
  scale_x_continuous(breaks = seq(1996, 2016, 2))+ scale_y_continuous(breaks = seq(0, 55000000, 1000000))+
  coord_cartesian(ylim=c(0,5500000)) +
  xlab('Survey Year') + ylab('Total LEGAL biomass adj')+
  ggtitle('Simulation 1 (2015 survey areas): total LEGAL biomass (lb)')
```

#### Figure 4: 
```{r figure4, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, comment=""}
ggplot(sim2015mature_adj, aes(Year_Survey, total_lb, color = type)) + geom_point(size=2) +geom_smooth() +
  scale_color_tableau() +
  scale_x_continuous(breaks = seq(1996, 2016, 2))+ scale_y_continuous(breaks = seq(0, 8000000, 1000000))+
  coord_cartesian(ylim=c(0,8000000)) +
  xlab('Survey Year') + ylab('Total MATURE biomass adj')+
  ggtitle('Simulation 1 (2015 survey areas): total MATURE biomass (lb)')
```


### Simulation 2: Estimating Tanner crab abundance using only RKC survey areas
This simulation uses only the red king crab survey areas to estimate the biomass for Tanner crab, it does NOT include any Tanner crab areas.  This would be an extreme example if the Tanner crab survey was cut in its entirety.

Average percent difference for legal biomass in Sim 2
```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE, comment=""}
simRKC2_adj <- survey_sim (dat4, areas_RKC_only)
round(mean (simRKC2_adj$per_diff[20:38])*100,4)
```
Average percent difference for mature biomass in Sim 2
```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE, comment=""}
simRKC2mature_adj <- survey_sim_mature (dat5, areas_RKC_only)
round(mean (simRKC2mature_adj$per_diff[20:38])*100,4)
#ls()
```

The total biomass for both legal and mature crab from Simulation 2 (S) is visually represented in the figures below (Figure 5 & 6), along with the total biomass from the "known (K)" survey data. Simulation 2 uses only survey biomass data from the red king crab surveys (RKC) to estimate Tanner crab biomass. Figures 5 & 6 show that using on the red king crab data tends to over estimate tanner crab abundance in higher years and under estimate abundance in low years.  This will be helpful in formation if only the red crab data is used to calculate abundance in the future.

#### Figure 5:
```{r figure5, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, comment=""}
ggplot(simRKC2_adj, aes(Year_Survey, total_lb, color = type)) + geom_point(size=2) +geom_smooth() +
  scale_color_tableau() +
  scale_x_continuous(breaks = seq(1996, 2016, 2))+ scale_y_continuous(breaks = seq(0, 55000000, 1000000))+
  coord_cartesian(ylim=c(0,5500000)) +
  xlab('Survey Year') + ylab('Total LEGAL biomass adj')+
  ggtitle('Simulation 2 (RKC survey areas only): total LEGAL biomass (lb)')
```

#### Figure 6: 
```{r figure6, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, comment=""}
ggplot(simRKC2mature_adj, aes(Year_Survey, total_lb, color = type)) + geom_point(size=2) +geom_smooth() +
  scale_color_tableau() +
  scale_x_continuous(breaks = seq(1996, 2016, 2))+ scale_y_continuous(breaks = seq(0, 8000000, 1000000))+
  coord_cartesian(ylim=c(0,8000000)) +
  xlab('Survey Year') + ylab('Total MATURE biomass adj')+
  ggtitle('Simulation 2 (RKC survey areas only): total MATURE biomass (lb)')
```


### Simulation 3: 2015 survey areas using only Tanner crab leg 1 (removing leg 2)
Simulation 3 builds off the 2015 survey areas sampled.  The next step would be to eliminate one of the Tanner crab survey legs.  In this simulation leg 2 was eliminated, this removes Thomas Bay and Holkham Bay from the surveyed areas.

Average percent difference for legal biomass in Sim 3
```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE, comment=""}
sim_areas1_adj <- survey_sim(dat4, areas_1)
round(mean (sim_areas1_adj$per_diff[20:38])*100,4)
#ls()
```
Average percent difference for mature biomass in Sim 3
```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE, comment=""}
sim_areas1mature_adj <- survey_sim_mature(dat5, areas_1)
round(mean (sim_areas1mature_adj$per_diff[20:38])*100,4)
#ls()
```

The total biomass for both legal and mature crab from Simulation 3 (S) is visually represented in the figures below (Figure 7 & 8), along with the total biomass from the "known (K)" survey data. Simulation 3 uses the survey areas used in 2015 with the removal of leg 2 (thomas bay and holkham bay) of the Tanner crab survey.  

Survey areas included in this simulation are: areas_1 <- c("EI" , "GB" , "GLB" ,"ICY" ,"LS",  "NJ" , "PB" , "PS",  "SC" , "SP" ).

#### Figure 7: 
```{r figure7, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, comment=""}
ggplot(sim_areas1_adj, aes(Year_Survey, total_lb, color = type)) + geom_point(size=2) +geom_smooth() +
  scale_color_tableau() +
  scale_x_continuous(breaks = seq(1996, 2016, 2))+ scale_y_continuous(breaks = seq(0, 55000000, 1000000))+
  coord_cartesian(ylim=c(0,5500000)) +
  xlab('Survey Year') + ylab('Total LEGAL biomass adj')+
  ggtitle('Simulation 3 (2015 areas and leg 1 TCS): total LEGAL biomass (lb)')
```

#### Figure 8:
```{r figure8, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, comment=""}
ggplot(sim_areas1mature_adj, aes(Year_Survey, total_lb, color = type)) + geom_point(size=2) +geom_smooth() +
  scale_color_tableau() +
  scale_x_continuous(breaks = seq(1996, 2016, 2))+ scale_y_continuous(breaks = seq(0, 8000000, 1000000))+
  coord_cartesian(ylim=c(0,8000000)) +
  xlab('Survey Year') + ylab('Total MATURE biomass adj')+
  ggtitle('Simulation 3 (2015 areas and leg 1 TCS): total MATURE biomass (lb)')
```

### Simulation 4: 2015 survey areas using only Tanner crab leg 2 (removing leg 1)
Simulation 4 also builds off the 2015 survey areas sampled.  The next step would be to eliminate one of the Tanner crab survey legs.  In this simulation leg 1 was eliminated, this removes Glacier Bay and Icy Strait from the surveyed areas.

Average percent difference for legal biomass in Sim 4
```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE, comment=""}
areas_2 <- c("EI" , "GB" , "HB"  ,"LS",  "NJ" , "PB" , "PS",  "SC" , "SP" , "TB")
  ### those used in 2015 minus GLB and ICY
sim_areas2_adj <- survey_sim(dat4, areas_2)
round(mean (sim_areas2_adj$per_diff[20:38])*100,4)
#ls()
```
Average percent difference for mature biomass in Sim 4
```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE, comment=""}
sim_areas2mature_adj <- survey_sim_mature(dat5, areas_2)
round(mean (sim_areas2mature_adj$per_diff[20:38])*100,4)
#ls()
```

The total biomass for both legal and mature crab from Simulation 4 (S) is visually represented in the figures below (Figure 9 & 10), along with the total biomass from the "known (K)" survey data. Simulation 4 uses the survey areas used in 2015 with the removal of leg 1 (glacier bay and icy strait) of the Tanner crab survey. Although the average percent difference is low in this simulation the simulation abundance trend is overall more variable than previous simulations.  

Survey areas included in this simulation are: areas_2 <- c("EI" , "GB" , "HB"  ,"LS",  "NJ" , "PB" , "PS",  "SC" , "SP" , "TB")


#### Figure 9: 
```{r figure9, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, comment=""}
ggplot(sim_areas2_adj, aes(Year_Survey, total_lb, color = type)) + geom_point(size=2) +geom_smooth() +
  scale_color_tableau() +
  scale_x_continuous(breaks = seq(1996, 2016, 2))+ scale_y_continuous(breaks = seq(0, 55000000, 1000000))+
  coord_cartesian(ylim=c(0,5500000)) +
  xlab('Survey Year') + ylab('Total LEGAL biomass adj')+
  ggtitle('Simulation 4 (2015 areas and leg 2 TCS): total LEGAL biomass (lb)')
```

#### Figure 10:
```{r figure10, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, comment=""}
ggplot(sim_areas2mature_adj, aes(Year_Survey, total_lb, color = type)) + geom_point(size=2) +geom_smooth() +
  scale_color_tableau() +
  scale_x_continuous(breaks = seq(1996, 2016, 2))+ scale_y_continuous(breaks = seq(0, 8000000, 1000000))+
  coord_cartesian(ylim=c(0,8000000)) +
  xlab('Survey Year') + ylab('Total MATURE biomass adj')+
  ggtitle('Simulation 4 (2015 areas and leg 2 TCS): total MATURE biomass (lb)')
```


###Table 3: Average % differences of total biomass for simulations 

```{r, echo=FALSE}
# table to summarize the average % difference  over all years for each simulation
#sim2015_adj$per_diff
#sim2015_adj$per_diff[20:38]
#mean (sim2015_adj$per_diff[20:38])

#legal average % difference
sim2015_adj_avg <- round(mean (sim2015_adj$per_diff[20:38])*100,2)
simRKC2_adj_avg <- round(mean (simRKC2_adj$per_diff[20:38])*100,2)
sim_areas1_adj_avg <- round(mean (sim_areas1_adj$per_diff[20:38])*100,2)
sim4_adj_avg_legal <- round(mean (sim_areas2_adj$per_diff[20:38])*100,2)
#mature average % difference

#per_diff <- c(sim2015_adj_avg, simRKC2_adj_avg, sim_areas1_adj_avg)
sim1_mature <- round(mean (sim2015mature_adj$per_diff[20:38])*100,2)
sim2_mature <- round(mean (simRKC2mature_adj$per_diff[20:38])*100,2)
sim3_mature <- round(mean (sim_areas1mature_adj$per_diff[20:38])*100,2)
sim4_mature <-round(mean (sim_areas2mature_adj$per_diff[20:38])*100,2)
  
table1 <- matrix(c(sim2015_adj_avg, simRKC2_adj_avg, sim_areas1_adj_avg, sim4_adj_avg_legal, sim1_mature, sim2_mature, sim3_mature, sim4_mature), ncol =4, byrow=TRUE)
colnames(table1) <- c("Sim 1", "Sim 2", "Sim 3", "Sim 4")
rownames(table1) <- c("legal", "mature")
#table1
####

```

```{r pander3, echo = FALSE, comment=""}
#head(dat2)
# using percent for each area from the last 10 years of the survey - percent_survey_area
panderOptions("digits", 2)
pander(table1)
#ls()
```
Average percent differenc can be misleading since large difference above or below the known biomass trend can cancel each other out, creating a low average percent difference when large actual differences are occuring.  These simulations should be interpreted with caution.

###Future work:

1) Simulations that allow for different areas to be sampled in each year

2) Simulations for red king crab survey


